### 2012-11-07 thesis/tex/1_introduction.tex
Almost all correction issues of Andreas and Alwin are realized now (except the ones of Alwin I couldn't read). Chapter 4 and 6 have a new structure.

Safety critical robot applications require extensive testing or formal verification in order to achieve adequate safe and predictable behaviour.
Even if a program does not control actuators itself and thus cannot directly cause any damage, its output might still be a trigger for dangerous actions involving several actors.
Imagine a medication reminder application running on a service robot which guides a person through the process of medication intake, as investigated in the healthcare robotics project at the
\begin{wrapfigure}{r}{0.58\textwidth}
  \centering
  \includegraphics[width=0.56\textwidth]{cafero_being_used}
  \caption{Service robot being used by older person~\cite{robostudio}.}
  \label{fig:cafero_being_used}
\end{wrapfigure}
University of Auckland, New Zealand \cite{jayawardena12:_desig}. All interaction is guided by showing textual instructions on a display, and by speech generation. An error in the program logic could cause an already taken medication to be reminded again and may injure a patient with Alzheimer's disease by causing a medication overdose.
Scientists are working on applications such as the medication reminder~\cite{p11:_feasib} which run on mobile robots serving in nursing homes for the elderly. Equipped with a touch display and several external devices such as a blood pressure measurement tool the robots aim to support and entertain the elderly in their daily activities~\cite{jayawardena12:_desig,5649910}.

With service robots coexisting with people and acting within their work\-spa\-ces, coping with reliability and safety issues is essential for trust and acceptance of these robots. In some cases safety certifications based on international standards for functional safety might be even required before robots get released for use or obtain concession for sale. One such international standard is IEC 61508~\cite{iec61508}, a basic functional safety standard targeting all kinds of industry.
ISO 13482~\cite{iso13482, iso13482-2} is still under development and is intended to be a harmonised European standard for safety requirements for robots in personal care applications.
However, considering functional safety while developing service robots is both complex and difficult; maybe one reason for the absense of safety checks and warranties in the current healthbot versions at the University of Auckland.
But facing the fact that safety requirements for service robots are expected to increase in future, there is a plan of slowly integrating safety functionality into the healthcare robotics project as a next step starting with the concepts introduced in this paper.

@@

Unfortunately, supplying an easy-to-use editor for constraint creation doesn't guarantee adequate thinking about sufficent constraints by the developer. Unmotivated or just unexperienced developers may miss important constraints needed in order to achieve a certain safety level.
To support the user in finding significant constraints it might be useful to automatically compute constraint suggestions which make true testimonies about the current designed program. First of all the generated constraints provide an opportunity for the developer to identify reasonable constraints as well as contradictions between constraints and specification. The latter would mean there are errors in the program which lead to undesired constraints. Furthermore, once constraints are created and checked for sanity they can be validated after every program change and thus ensure integrity during the development process. Chapter~\ref{chap:automatedgenerationofsafetyconstraints} introduces a heuristics for finding reasonable safety constraints based on state machine definitions that describe robots' behaviours.

Both ideas have been integrated into Robostudio in order to simplify respectively facilitate the use of safety mechanisms for application development for service robots. Thereby the desired safety certification for the healthcare service robots can move closer one step.

This work starts with background information about the healthcare domain, short explanations of common safety mechanisms and insights into related work in chapter~\ref{chap:background}. After the goals have been mentioned in chapter~\ref{chap:goals}, the visual formalisms and the automated constraint generation are introduced in chapters~\ref{chap:visualformalismsforsafetyconstraints} and~\ref{chap:automatedgenerationofsafetyconstraints}.
A prototype implementation is demonstrated in chapter~\ref{chap:theltlcreatorprototype}, and a test scenario is described in chapter~\ref{chap:testscenarioandevaluation} where the presented tools get evaluated.
Chapter~\ref{chap:conclusionandfuturework} gives a short conclusion and an outlook how the presented work could be continued.

>>>>

Safety critical robot applications require extensive testing or formal verification in order to achieve adequate safe and predictable behaviour.
Even if a program does not control actuators itself and thus cannot directly cause any damage, its output might still be a trigger for dangerous actions involving several actors.
Imagine a medication reminder application running on a service robot which guides a person through the process of medication intake, as investigated in the healthcare robotics project at the
\begin{wrapfigure}{r}{0.58\textwidth}
  \centering
  \includegraphics[width=0.56\textwidth]{cafero_being_used}
  \caption{Service robot being used by older person~\cite{robostudio}.}
  \label{fig:cafero_being_used}
\end{wrapfigure}
University of Auckland, New Zealand \cite{jayawardena12:_desig}. All interaction is guided by showing textual instructions on a display, and by speech generation. An error in the program logic could cause an already taken medication to be reminded again and may injure a patient with Alzheimer's disease by causing a medication overdose.
Scientists are working on applications such as the medication reminder~\cite{p11:_feasib} which run on mobile robots (so called healthbots) serving in nursing homes for the elderly. Equipped with a touch display and several external devices such as a blood pressure measurement tool the robots aim to support and entertain the elderly in their daily activities~\cite{jayawardena12:_desig,5649910}.

With service robots coexisting with people and acting within their work\-spa\-ces, coping with reliability and safety issues is essential for trust and acceptance of these robots. In some cases safety certifications based on international standards for functional safety might be even required before robots get released for use or obtain concession for sale. One such international standard is IEC 61508~\cite{iec61508}, a basic functional safety standard targeting all kinds of industry.
ISO 13482~\cite{iso13482, iso13482-2} is still under development and is intended to be a harmonised European standard for safety requirements for robots in personal care applications.
However, considering functional safety while developing service robots is both complex and difficult; maybe one reason for the absense of safety checks and assurances in the current healthbot versions at the University of Auckland.
But facing the fact that safety requirements for service robots are expected to increase in future, there is a plan of slowly integrating safety functionality into the healthcare robotics project as a next step starting with the concepts introduced in this paper.

@@

Unfortunately, supplying an easy-to-use editor for constraint creation does not guarantee adequate thinking about sufficent constraints by the developer. Unmotivated or just unexperienced developers may miss important constraints needed in order to achieve a certain safety level.
To support the user in finding significant constraints it might be useful to automatically compute constraint suggestions which make true testimonies about the current designed program. First of all the generated constraints provide an opportunity for the developer to identify reasonable constraints as well as contradictions between constraints and specification. The latter would mean there are errors in the program which lead to undesired constraints. Furthermore, once constraints are created and checked for sanity they can be validated after every program change and thus ensure integrity during the development process. Chapter~\ref{chap:automatedgenerationofsafetyconstraints} introduces a heuristics for finding reasonable safety constraints based on state machine definitions that describe robots' behaviours.

Both ideas, the viual language and the automated constraint generation, have been developed and integrated by the author into Robostudio in order to simplify respectively facilitate the use of safety mechanisms for application development for service robots. Thereby the desired safety certification for the healthcare service robots can move closer by one step.

This work starts with background information about the healthcare domain, short explanations of common safety mechanisms and insights into related work in chapter~\ref{chap:background}. After the goals have been described in chapter~\ref{chap:goals}, the visual formalisms and the automated constraint generation are introduced in chapters~\ref{chap:visualformalismsforsafetyconstraints} and~\ref{chap:automatedgenerationofsafetyconstraints}.
A prototype implementation is demonstrated in chapter~\ref{chap:theltlcreatorprototype}, and a test scenario is described in chapter~\ref{chap:testscenarioandevaluation} where the presented tools get evaluated.
Chapter~\ref{chap:conclusionandfuturework} gives a short conclusion and an outlook how the presented work could be continued.

### 2012-11-07 thesis/tex/2_background.tex
correction update, chapter 4 has a new structure
Almost all correction issues of Andreas and Alwin are realized now (except the ones of Alwin I couldn't read). Chapter 4 and 6 have a new structure.

The visual programming environment used for the programming of these robots is presented in section~\ref{sec:robostudio}.
For the understanding of safety concepts which this work is based on, a short introduction about functional safety is given in section~\ref{sec:behaviourchecking}. In section~\ref{sec:relatedwork} other work and programs related to this work are examined.

@@

%\begin{wrapfigure}{r}{0.38\textwidth}
%  \centering
%  \includegraphics[width=0.34\textwidth]{populationpyramide}
%  \caption{Age structure.}%Population pyramide of germany.}
%  \label{fig:populationpyramide}
%\end{wrapfigure}
In some countries, among New Zealand and Germany, the average age of population is constantly increasing. Owing to excellent achievements in medicine as well as higher living standards, humans can enjoy longer lifes. Also decreasing birth rates contribute to an upward drift of the dominating age range. As a result, the industrial sectors of professional health care and social institutions are required more than ever.
However, a strong deficit of professionals is denoted in the healthcare branch and availability is far behind demand. One reason for this might be below average low salaries for employees in the healthcare sector. But, just raising the salary isn't leading to the desired results since the majority of the older people can't even afford a nurse to today's prices.

Aiming for fillig the constantly increasing gap in professional personnel for healthcare of the elderly and bypassing the financial burden, service robots are supposed to more and more undertake the task of care.
There are lots of possible tasks a robot could do such as taking the blood pressure, guiding medication intake, detecting falls or just entertaining with music, video or internet.
This challenge as a goal, the healthcare robotics team at the University of Auckland researches this topic and builds service robots for supporting the elderly in their daily life.

The two newest robots IrobiQ and Cafero are shown in figure~\ref{fig:irobiq_cafero}.
These mobile 
\begin{wrapfigure}{r}{0.60\textwidth}
  \centering
  \includegraphics[width=0.56\textwidth]{irobiq_cafero}
  \caption{IrobiQ and Cafero, two robots of the healtcare project.}
  \label{fig:irobiq_cafero}
\end{wrapfigure}
robots are equipped with a touch display for presenting screens and receiving user input. Furthermore, they are equipped with additional external tools such as the blood pressure measurement device.
Applications running on the robot use the touch display to present screen dialogs to the user and use speech synthesis in order to give also accoustic feedback. User inputs or response from devices cause dialogs to change. Figure~\ref{fig:screenflow_example} presents a small example of such a screen-flow based application, which uses response from a camera and user input for navigating through the screen-flow.

@@

There is a program interpreter running on the robots which can load and execute program files. Screen dialogs get generated and displayed on the touch screen.
%This makes the program behaviour replaceable and maintenance can be done easily.
The interpreter processes programs written in Robot Behaviour Description Language (RBDL), a domain specific language (DSL) based on XML, which has been developed particularly for the healthcare robotics applications. It allows defining state machine based program behaviour and creating UI elements for screen visualizations. An example implementation of one state in RBDL is shown in listing~\ref{lst:RBDL}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{screenflow_example} 
  \caption{Robot screen-flow dialog based interaction example~\cite{robostudio}.}
  \label{fig:screenflow_example}
\end{figure}

@@

\begin{lstlisting}[float = htbp, language=XML, captionpos=b, breaklines=true, showspaces=false, showtabs=false, tabsize=2, caption=Example of a state defined by RBDL~\cite{robostudio}., label=lst:RBDL]
<state no="84">
	<backgroundactions>
		<rocosmessage type="EVENT MESSAGE" senderid="RCP" receiverid="NA" name="FDSessionStart">
			<parameter vartype="text" type="unsigned int" name="id">1</parameter>
			<parameter type="string" name="" />
		</rocosmessage>
	</backgroundactions>
	<screen>
		<components>
			<button label="START" width="250" height="100" x="387" y="600" textsize="40">
				<event name="clicked">
					<action preconditions="no" name="transition">
						<parameter>
							<type>state</type>
							<name>n</name>
							<value>86</value>
						</parameter>
					</action>
				</event>
			</button>
		</components>
	</screen>
	<expectedevents>
		<event name="TimeOut">
			<action preconditions="no" name="transition">
				<parameter>
					<type>state</type>
					<name>n</name>
					<value>VARFirstScreen</value>
				</parameter>
			</action>
		</event>
	</expectedevents>
</state>
\end{lstlisting}

@@

For this work the most important thing about the RBDL to remember is that it can define state machine behaviour with states, transitions and events. This fact was the basis for later decisions regarding used safety mechanisms.

@@

In the beginning all programming of the robot behaviour was done by directly editing the XML code mentioned in the previous section by using a text editor. But huge code files and occasional code edits made further maintenance and change requests difficult up to impossible to realise. For this reason, Chandan Datta, PhD student at the University of Auckland, developed a visual programming environment for developing robot behaviour on top of RBDL: Robostudio~\cite{robostudio} allows to easily edit the program behaviour on a visual layer and generates the corresponding program file containing the RBDL code fully automatically. This file can be downloaded to the robot and executed by the interpreter. Figure~\ref{fig:robostudio_proceeding} illustrates the steps of robot behaviour development.

@@

Robostudio is an editor fully written in Java and implemented as a NetBeans rich client application.
Several windows and views provide visual tools for editing and understanding robot behaviour as well as screen dialog design. As depicted in figure~\ref{fig:robostudio_vpe}, the editor integrates a \emph{State Navigator Window} (1) in the top left corner where all existing states are listed. Below an overview about all incoming and outgoing transitions is given. New states can be created and existing states can be deleted. A click on one particular state id in the \emph{State Navigator Window} will cause all other components to show all possible information regarding the selected state.
The \emph{Expected Events Editor Window} (2) in the bottom left can be used for specifying the expected events and their effects.
Heart and center of the editor is the \emph{UI Component Layout Editor Window} (3). It renders the screen dialog of the selected state and gives a preview of the screen presented on the robot during runtime. Components such as buttons, text boxes or images can be added, changed or removed via drag and drop.
They are provided by the \emph{UI Components Palette Window} (4) on the right side where the user can choose from all supported UI components.
The \emph{Background Actions Editor Window} (5) lets the user define background actions, which are executed transparently to the user such as accessing external devices or sending messages.
Aiming to support the developer with helpful graphical tools, the \emph{State Transition Visualization Window} (6) gives an overview about all connections towards and from the selected state. It helps to quickly get an understanding of the local program behaviour.

@@

The use of software is versatile from text editing programs running on personal computers, over control software for high-precision applications in aeronautics, right up to trigger mechanisms for deathly weapons. For most of them safety properties are irrelevant, but a few are ranked highly dangerous to their environment and also human lifes. In order to eliminate software malfunction there are different mathematical concepts for verifying software behaviour.
One of them is model checking wich allows checking state machine programs for functional safety. Since the healthbot applications mentioned in section~\ref{sec:healthbotapplication} are realised wth state machines, this concept of behaviour checking is applicable and important for our kind of programs. At first the basic idea of state machines is described in section~\ref{sec:statemachines}, followed by an intorduction into model checking in section~\ref{sec:modelcheckingandltl}.

@@

\begin{description}
	\item[$\varphi \mathcal{U} \psi$] The ``UNTIL'' operator makes $\varphi$ true until the first occurrence of a state where $\psi$ is true. Besides, $\psi$ will eventually be true.
	\item[$\varphi \mathcal{R} \psi$] It expresses that $\psi$ is true through the first occurrence of a state where $\varphi$ is true. Its meaning is $\varphi$ ``RELEASES'' $\psi$.
	\item[$\varphi \mathcal{W} \psi$] ``WEAK UNTIL'' represents the same as ``UNTIL'', except that an occurrence of $\psi$	is not necessary. In this case, $\varphi$ is true infinetely.
\end{description}

>>>>

The visual programming environment used for the programming of these robots is presented in section~\ref{sec:robostudio}.
For the understanding of safety concepts which this work is based on, a short introduction about functional safety is given in section~\ref{sec:behaviourchecking}. In section~\ref{sec:relatedwork} other works and programs related to this work are examined.

@@

%\begin{wrapfigure}{r}{0.38\textwidth}
%  \centering
%  \includegraphics[width=0.34\textwidth]{populationpyramide}
%  \caption{Age structure.}%Population pyramide of germany.}
%  \label{fig:populationpyramide}
%\end{wrapfigure}
In some countries, among New Zealand and Germany, the average age of population is constantly increasing. Owing to excellent achievements in medicine as well as higher living standards, humans can enjoy longer lifes. Also decreasing birth rates contribute to an upward drift of the dominating age range. As a result, the industrial sectors of professional health care and social institutions are required more than ever.
However, a strong deficit of professionals is denoted in the healthcare branch and availability is far behind demand. One reason for this might be below average low salaries for employees in the healthcare sector. But, just raising the salary will not lead to the desired results since the majority of the older people can not even afford a nurse to today's prices.

Aiming for fillig the constantly increasing gap in professional personnel for healthcare of the elderly and bypassing the financial burden, service robots are supposed to undertake more and more the task of care.
There are lots of possible tasks a robot could do such as taking the blood pressure, guiding medication intake, detecting falls or just entertaining with music, video or internet.
This challenge as a goal, the healthcare robotics team at the University of Auckland researches this topic and develops service robots for supporting the elderly in their daily life.

The two newest robots IrobiQ and Cafero are shown in figure~\ref{fig:irobiq_cafero}.
These mobile 
\begin{wrapfigure}{r}{0.60\textwidth}
  \centering
  \includegraphics[width=0.56\textwidth]{irobiq_cafero}
  \caption{IrobiQ and Cafero, two robots of the healthcare project.}
  \label{fig:irobiq_cafero}
\end{wrapfigure}
robots are equipped with a touch display for presenting screens and receiving user input. Furthermore, they are equipped with additional external tools such as the blood pressure measurement device.
Applications running on the robots use the touch display to present screen dialogs to the user and use speech synthesis in order to give also accoustic feedback. User inputs or responses from devices cause dialogs to change. Figure~\ref{fig:screenflow_example} presents a small example of such a screen-flow based application, which uses response from a camera and user input for navigating through the screen-flow.

@@

There is a program interpreter running on the robots which can load and execute program files. Screen dialogs get generated and displayed on the touch screen.
%This makes the program behaviour replaceable and maintenance can be done easily.
The interpreter processes programs written in Robot Behaviour Description Language (RBDL), a domain specific language (DSL) based on XML, which has been developed particularly for the healthcare robotics applications. It allows defining state machine based program behaviour and creating user interface (UI) elements for screen visualizations. An example implementation of one state in RBDL is shown in listing~\ref{lst:RBDL}.

\begin{figure}[htbp]
  \centering
  \includegraphics[width=\linewidth]{screenflow_example} 
  \caption{Interaction example based on robot screen-flow dialogs~\cite{robostudio}.}
  \label{fig:screenflow_example}
\end{figure}

@@

\begin{lstlisting}[float = htbp, language=XML, captionpos=b, breaklines=true, showspaces=false, showtabs=false, tabsize=2, caption=Example of a state defined with RBDL~\cite{robostudio}., label=lst:RBDL]
<state no="84">
	<backgroundactions>
		<rocosmessage type="EVENT MESSAGE" senderid="RCP" receiverid="NA" name="FDSessionStart">
			<parameter vartype="text" type="unsigned int" name="id">1</parameter>
			<parameter type="string" name="" />
		</rocosmessage>
	</backgroundactions>
	<screen>
		<components>
			<button label="START" width="250" height="100" x="387" y="600" textsize="40">
				<event name="clicked">
					<action preconditions="no" name="transition">
						<parameter>
							<type>state</type>
							<name>n</name>
							<value>86</value>
						</parameter>
					</action>
				</event>
			</button>
		</components>
	</screen>
	<expectedevents>
		<event name="TimeOut">
			<action preconditions="no" name="transition">
				<parameter>
					<type>state</type>
					<name>n</name>
					<value>VARFirstScreen</value>
				</parameter>
			</action>
		</event>
	</expectedevents>
</state>
\end{lstlisting}

@@

Very important for this work is a fundamental feature of RBDL, the ability to define state machine behaviour with states, transitions and events. This fact was the basis for later decisions regarding the applied safety mechanisms.

@@

In the beginning all programming of the robot behaviour was done by directly editing the XML code mentioned in the previous section by using a text editor. However, huge code files and occasional code edits made further maintenance and change requests difficult up to impossible to realise. For this reason, Chandan Datta, PhD student at the University of Auckland, developed a visual programming environment for developing robot behaviour on top of RBDL. This environment- it is called Robostudio~\cite{robostudio} - allows to edit easily the program behaviour on a visual layer and generates the corresponding program file containing the RBDL code fully automatically. This file can be downloaded to the robot and executed by the interpreter. Figure~\ref{fig:robostudio_proceeding} illustrates the steps of robot behaviour development.

@@

Robostudio is an editor fully written in Java and implemented as a NetBeans rich client application.
Several windows and views provide visual tools for editing and understanding robot behaviour as well as screen dialog design. As depicted in figure~\ref{fig:robostudio_vpe}, the editor integrates a \emph{State Navigator Window} (1) in the top left corner where all existing states are listed. Below an overview about all incoming and outgoing transitions is given. New states can be created and existing states can be deleted. A click on one particular state id in the \emph{State Navigator Window} will cause all other components to show all possible information regarding the selected state.
The \emph{Expected Events Editor Window} (2) in the bottom left can be used for specifying the expected events and their effects.
Heart and center of the editor is the \emph{UI Component Layout Editor Window} (3). It renders the screen dialog of the selected state and gives a preview of the screen presented on the robot during runtime. Components such as buttons, text boxes or images can be added, changed or removed via drag and drop.
They are provided by the \emph{UI Components Palette Window} (4) on the right side where the developer can choose from all supported UI components.
The \emph{Background Actions Editor Window} (5) lets the developer define background actions, which are executed transparently to the developer such as accessing external devices or sending messages.
Aiming to support the developer with helpful graphical tools, the \emph{State Transition Visualization Window} (6) gives an overview about all connections towards and from the selected state. It helps to get quickly an understanding of the local program behaviour.

@@

The use and application of software is versatile and varies from text editing programs running on personal computers, over control software for high-precision applications in aeronautics, right up to trigger mechanisms for deathly weapons. For most of them safety properties are irrelevant, but a few are ranked highly dangerous to their environment and also to human lifes. In order to eliminate software malfunction there are different mathematical concepts for verifying software behaviour.
One of them is model checking which allows checking state machine programs for functional safety. Since the healthbot applications mentioned in section~\ref{sec:healthbotapplication} are realised wth state machines, this concept of behaviour checking is applicable and important for our kind of programs. At first the basic idea of state machines is described in section~\ref{sec:statemachines}, followed by an introduction into model checking in section~\ref{sec:modelcheckingandltl}.

@@

\begin{description}
	\item[$\varphi \mathcal{U} \psi$] The ``UNTIL'' operator makes $\varphi$ true at least until the first occurrence of a state where $\psi$ is true. Besides, $\psi$ will eventually be true.
	\item[$\varphi \mathcal{R} \psi$] It expresses that $\psi$ is true through the first occurrence of a state where $\varphi$ is true. Its meaning is $\varphi$ ``RELEASES'' $\psi$.
	\item[$\varphi \mathcal{W} \psi$] ``WEAK UNTIL'' represents the same as ``UNTIL'', except that an occurrence of $\psi$	is not necessary. In this case, $\varphi$ is true infinetely.
\end{description}

### 2012-11-07 thesis/tex/4_visualformalismsforsafetyconstraints.tex
Almost all correction issues of Andreas and Alwin are realized now (except the ones of Alwin I couldn't read). Chapter 4 and 6 have a new structure.

\begin{description}
	\item[(a)] \emph{AND} operator: $\varphi \wedge \psi$.
	\item[(b)] \emph{OR} Operator: $\varphi \vee \psi$.
	\item[(c)] \emph{IF} operator: $\varphi \rightarrow \psi$.\\Instead of an \emph{IMPLIES} operator an \emph{IF} operator is provided. Its meaning seems to be more intuitive for non-experts since it is a common construct in almost every programming language.
	\item[(d)] \emph{NOT} operator: $\neg \varphi$.
	\item[(e)] Proposition: $\rho$.\\Until now there is only the \emph{state proposition} type, which gives evidence about the currently active state. Other types such as numeric or string equations may be added but are less important for the healthcare subject.
\end{description}

@@

\subsection{Design decisions}

>>>>

\begin{description}
	\item[(a)] \emph{AND} operator: $\varphi \wedge \psi$.\\This conjunction evaluates to true only when both $\varphi$ and $\psi$ are true.
	\item[(b)] \emph{OR} Operator: $\varphi \vee \psi$.\\At least one $\varphi$ or $\psi$ being true makes this construct true. The result is false when both parameters are false.
	\item[(c)] \emph{IF} operator: $\varphi \rightarrow \psi$.\\Instead of an \emph{IMPLIES} operator an \emph{IF} operator is provided. Its meaning seems to be more intuitive for non-experts since it is a common construct in almost every programming language.
	\item[(d)] \emph{NOT} operator: $\neg \varphi$. This operator negates the value of $\varphi$.
	\item[(e)] Proposition: $\rho$.\\Until now there is only the \emph{state proposition} type, which gives evidence about the currently active state. Other types such as numeric or string equations may be added but are less important for the healthcare subject.
\end{description}

@@

\subsection{Design decisions}
\label{sec:designdecisions}
